Excuse me, do you have a moment to talk about version control?

### 2017-05-18 README.Rmd
Work on the yaml

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- affiliation: RStudio and the Department of Statistics, University of British Columbia
  name: Jennifer Bryan
  thanks: The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton and Colin Rundel.
blinded: 0
output:
  rticles::asa_article:
    pandoc_args: --listings
  github_document:
    toc: yes
keywords: version control
abstract: Abstract abstract abstract.
---

```{r}
is_github_document <-
  knitr::opts_knit$get("rmarkdown.pandoc.to") == "markdown_github"
```

@@

Why would a practicing statistician use version control, such as Git? And what is the point of hosting your work online, e.g., on GitHub? Could the gains possibly justify the inevitable pain?

@@

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it. It's not a separate, burdensome task you are tempted to neglect.
  * Collaboration becomes much more structured, with powerful tools for asynchronous work and managing versions.
  * The marginal effort required to create a web presence for a project is negligible.
  * GitHub makes a fantastic course management system for courses that use R. You and your students can exchange actual working code and explore the associated results.
  * By using common mechanics across work modes (research, teaching, analysis), you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
authors:
- name: Jennifer Bryan
  affiliation: |
    RStudio and the Department of Statistics, University of British Columbia
  thanks: |
    The author gratefully acknowledges the constructive feedback from reviewers
    Nicholas Horton and Colin Rundel.
blinded: 0
output:
  rticles::asa_article: null
  github_document:
    toc: yes
keywords: version control
abstract: Abstract abstract abstract.
---

```{r include = FALSE}
## I temporarily embed some figures from the internet and LaTeX just. can't.
## deal. with. it.
is_github_document <-
  knitr::opts_knit$get("rmarkdown.pandoc.to") == "markdown_github"
```

@@

Why would a statistician use version control, such as Git? And what is the point of hosting your work online, e.g., on GitHub? Could the gains possibly justify the inevitable pain?

@@

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it. It's not a separate, burdensome task you are tempted to neglect.
  * Collaboration is much more structured, with powerful tools for asynchronous work and managing versions.
  * The marginal effort required to create a web presence for a project is negligible.
  * GitHub makes a fantastic course management system for courses that use R. You and your students can exchange actual working code and explore the associated results.
  * By using common mechanics across work modes (research, teaching, analysis), you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.
